### 2022-07-09 manuscript.Rmd
Update preprocessing

# Process EEG data
res <- pipeline$group_pipeline(
  vhdr_files = vhdr_files,
  log_files = logs,
  output_dir = output_dir,
  report_dir = NULL,
  downsample_sfreq = 125,
  bad_channels = "auto",
  ocular_correction = "auto",
  highpass_freq = 0.1,
  lowpass_freq = 40,
  triggers = c(221, 222),
  epochs_tmin = -0.5,
  epochs_tmax = 1.5,
  baseline_tmin = -0.2,
  baseline_tmax = 0.0,
  reject_peak_to_peak = 200,
  components = list(
    "name" = list("P1", "N170", "N400"),
    "tmin" = list(0.1, 0.15, 0.4),
    "tmax" = list(0.15, 0.2, 0.7),
    "roi" = list(
      c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
      c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
      c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
    )
  ),
  average_by = c("phase/condition"),
  perform_tfr = TRUE,
  tfr_subtract_evoked = FALSE,
  tfr_freqs = seq(4, 40, by = 1.0),
  tfr_cycles = seq(2, 20, by = 0.5),
  tfr_baseline_tmin = -0.45,
  tfr_baseline_tmax = -0.05,
  tfr_baseline_mode = "percent",
  perm_contrasts = list(
    c("Pre-insight/Informed", "Pre-insight/Naive"),
    c("Insight/Informed", "Insight/Naive"),
    c("Post-insight/Informed", "Post-insight/Naive")
  ),
  perm_tmin = 0.0,
  perm_tmax = 1.0,
  n_jobs = 1
)
```

@@

# Save models
saveRDS(models, models_file)
```

>>>>

# Process EEG data
res <- pipeline$group_pipeline(
  vhdr_files = vhdr_files,
  log_files = logs,
  output_dir = output_dir,
  report_dir = NULL,
  downsample_sfreq = 125,
  bad_channels = NULL,
  ocular_correction = "auto",
  highpass_freq = 0.1,
  lowpass_freq = 30,
  triggers = c(221, 222),
  epochs_tmin = -0.5,
  epochs_tmax = 1.5,
  baseline_tmin = -0.2,
  baseline_tmax = 0.0,
  reject_peak_to_peak = 200,
  components = list(
    "name" = list("P1", "N170", "N400"),
    "tmin" = list(0.1, 0.15, 0.4),
    "tmax" = list(0.15, 0.2, 0.7),
    "roi" = list(
      c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
      c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
      c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
    )
  ),
  average_by = c("phase/condition"),
  perform_tfr = TRUE,
  tfr_subtract_evoked = FALSE,
  tfr_freqs = seq(4, 40, by = 1.0),
  tfr_cycles = seq(2, 20, by = 0.5),
  tfr_baseline_tmin = -0.45,
  tfr_baseline_tmax = -0.05,
  tfr_baseline_mode = "percent",
  perm_contrasts = list(
    c("Pre-insight/Informed", "Pre-insight/Naive"),
    c("Insight/Informed", "Insight/Naive"),
    c("Post-insight/Informed", "Post-insight/Naive")
  ),
  perm_tmin = 0.0,
  perm_tmax = 1.0,
  n_jobs = 1
)
```

@@

# Save models
saveRDS(models, here(output_dir, "models.RDS"))
```
